A Kochen-Specker system has at least 22 vertices

### 2014-04-08 main.tex
Add bibliography
abstract and correct order of authors

% TODO this suggests only one result: the improved lower bound
%      reference to other results?
\title{A Kochen-Specker Vector System has at least 22 vertices}

\author{Bas Westerbaan}
\author{Sander Uijlen}
\affil{Institute for Computing and Information Sciences\\
       Radboud Universiteit Nijmegen\\
   \{\texttt{bwesterb},\texttt{suijlen}\}\texttt{@cs.ru.nl}}

@@

\begin{abstract}
    TODO
\end{abstract}

@@

>>>>

% TODO this suggests only one result: the improved lower bound
%      reference to other results?
\title{A Kochen-Specker system has at least 22 vertices}

\author{Sander Uijlen}
\author{Bas Westerbaan}

% TODO will we keep these @cs.ru.nl addresses?
\affil{Institute for Computing and Information Sciences\\
       Radboud Universiteit Nijmegen\\
   \{\texttt{bwesterb},\texttt{suijlen}\}\texttt{@cs.ru.nl}}

@@

\begin{abstract}
    A Kochen-Specker system is a set of points on the sphere,
    such that there is no~$\{0,1\}$-coloring such that
    at most one of two orthogonal points is assigned~$1$
    and of three pairwise orthogonal points exactly one
    is assigned~$1$.
    The existence of such a system is the basis of the Kochen-Specker
    and Free Will theorems.  At the time of writing, the smallest known
    KS system has 31 vectors.

    Arends, Ouaknine and Wampler have shown that a KS system has at least
    18 vectors, by reducing the problem to the existence of graphs
    with a certain topological embeddability and non-colorability property.
    Deciding embeddability and the sheer number of graphs on more than~$17$
    vertices, proved the bottleneck in their search.

    Continuing their effort, we restrict our enumeration to smaller class of
    graphs and develop a practical decision procedure for embeddability, to
    establish an improved lower bound of 22.
\end{abstract}

@@

\bibliography{main}{}
\bibliographystyle{plain}
